Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-03-15 manuscript.Rmd
first part of discussion

## Performance Verdict: It Works

Accuracy good compared to typical metrics of agreement, comparable to human agreement, in both proximal and distal comparisons.

>>>>

## Accurate Results in Challenging Circumstances

How did classification in the current investigation compare to prior work [@FranchakScott2021; @AiraksinenRasanen2020; @AiraksinenGallen2022]? Across body positions, median accuracy was `r metrics_lookup["Overall Accuracy", "median_Group"]`% for group models (Kappa = `r metrics_lookup["Kappa", "median_Group"]`) and `r metrics_lookup["Overall Accuracy", "median_Individual"]`% for individual models (Kappa = `r metrics_lookup["Kappa", "median_Individual"]`) during the proximal comparison. Although these accuracy and kappa values are slightly lower than in past work (accuracy 95-98%, kappas .93-.95), we note that those past values were obtained under ideal circumstances. A researcher applied the sensors in the lab [@FranchakScott2021; @AiraksinenRasanen2020] or home [@AiraksinenGallen2022] and set the stage for how infants and caregivers should interact. For example, both @FranchakScott2021 and @AiraksinenGallen2022 instructed the caregivers that the recorded sessions should mimic a "playtime", which would encourage more common activities that would be easier to classify (e.g., crawling and sitting on the floor) and discourage idiosyncratic and potentially more challenging activities (e.g., positioning in infant-specific furniture like exersaucers and walkers, sitting or lying for long periods while eating or nursing). Examining the timelines in Figure \@ref(fig:timelines) shows how much variability there is between and within sessions in the earlier parts of the recording that were used for training and testing. With the exception of the brief guided session at the start of the recording (which ensured that every infant spent at least a short amount of time in each body position), the majority of the recorded behavior was truly natural and "in the wild".

The challenge only increased in the distal comparison period. Since sessions were scheduled at convenient times to for the infant and caregiver, the transition from the proximal to distal period increased the odds that infants might need a nap, a snack/meal, or engage in a less typical activity (e.g., watching TV). Indeed, the distal comparison in Figure \@ref(fig:exemplar-timeline) contains a long period (almost 50 minutes) where the infant sat in a high chair eating lunch. With such a long delay in time from when the sensor garment was first put on, there is an increasing chance that sensors moved from their ideal positions. Regardless of these challenges, accuracy in the distal comparison continued to be strong. Barring two outliers (which we will discuss further), agreement was high for group (*r* = `r group_agree_cor_noout`) and individual models (*r* = `r split_agree_cor_noout`). Even at a finer timescale, most errors within 10-minute bins were less than 1 minute in total for all five body positions.

To put this in context, the reliability of human coders on the body position code was ~90%, putting model-predicted accuracy on a similar level to human coders. Acceptable inter-rater reliability in developmental psychology studies of motor behavior is greater than 80%; both group and individual model results exceed that standard for most sessions.
<!-- Reliability standard? -->
